---
title: "Exercise: Explore, Clean, and Wrangle Data"
author: "AT"
format: html
---

## About the data
The practice dataset is spiny lobster abundance, size, and fishing effort in the Santa Barbara area. Accessed June 29, 2023 from [https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-sbc.77.8](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-sbc.77.8)

## Setup
Adding libraries
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```


## Read and explore data
Lobster abundance data:
```{r}
lobster_abundance <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=f32823fba432f58f66c06b589b7efac6")
head(lobster_abundance)
```

Lobster fishing effort data:
```{r}
lobster_traps <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=66dd61c75bda17c23a3bce458c56ed84")
head(lobster_traps)
```
Initial exploration of abundance data:
```{r}
colnames(lobster_abundance)
summary(lobster_abundance)
```

Initial exploration of catch effort data:
```{r}
colnames(lobster_traps)
summary(lobster_traps)
```


## Exercise 1

## Exercise 2 

## Exercise 3

## Exercise 4

## Exercise 5

## Exercise 6